Uncertainty propagation in deep neural networks for sparse coding

### 2018-03-09 paper/BayesianLISTA.tex
required rewrite performed

Then derivatives of $Z$ are computed w.r.t the weights and Gaussian precision parameters of the factorised distribution and then they are used for updates. [REWRITE AND ADD ABOUT RECURRENT ESTIMATION]

>>>>

Parameters of the approximating posterior distribution are then updated with the derivates of this normalisation constant. [ADD ABOUT RECURRENT ESTIMATION]
